Performing graph-based clustering with rOpenScPCA

### 2024-11-15 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
fix header depth
fix wording

* Perform clustering
* Calculate QC metrics on clustering including:
  * Silhouette width
  * Neighborhood purity
  * Cluster stability, as measured with the Adjusted Rand Index
* Calculate QC metrics obtained with other tools, such as `Seurat`
* Save clustering results to an SCE or `Seurat`

@@

### Working with objects directly

>>>>

* Perform clustering
* Calculate QC metrics on clusters, including:
  * Silhouette width
  * Neighborhood purity
  * Cluster stability, as measured with the Adjusted Rand Index
* Calculate QC metrics on clusters obtained with other tools, such as `Seurat`
* Save clustering results to an SCE or `Seurat`

@@

## Working with objects directly
